%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%- Packages -%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%- Title formatting -%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%- Header / Footer -%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%- Document -%
\begin{document}
\onehalfspacing

%- Title block -%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Advertising \& Affiliate Disclosure}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%- Preamble & Keywords -%
\noindent\textbf{Preamble}\\
This Advertising \& Affiliate Disclosure explains how krisyotam.com may monetize content through various advertising, affiliate partnerships, sponsored content, and other commercial relationships. This disclosure is provided in the spirit of transparency and in accordance with the Federal Trade Commission (FTC) guidelines concerning the use of endorsements and testimonials in advertising, as well as similar regulations in other jurisdictions.

\vspace{0.75em}
\noindent\textit{Keywords:} Affiliate Links; Sponsored Content; Advertising; Commissions; Monetary Relationships

\vspace{1.5em}

%- Main sections -%
\section{General Advertising Disclosure}
krisyotam.com is a personal website that may generate income through various monetization methods. This income helps support the creation of content and maintenance of the website. Our commitment to editorial integrity means that advertising relationships do not dictate our content or opinions.

\section{Types of Commercial Relationships}

\subsection{Affiliate Links}
Some links on krisyotam.com are "affiliate links." This means that if you click on the link and subsequently make a purchase, we may receive a commission or other compensation at no additional cost to you. Affiliate programs we may participate in include, but are not limited to:
\begin{itemize}
  \item Amazon Associates Program
  \item Bookshop.org Affiliate Program
  \item Other book retailer affiliate programs
  \item Select software or digital product affiliate programs
\end{itemize}

Products or services mentioned with affiliate links are only recommended if we genuinely believe they may be of value or interest to our readers.

\subsection{Sponsored Content}
Occasionally, we may publish content that has been sponsored by a third party. Such content will be clearly marked as "Sponsored," "Sponsored Content," "Paid Partnership," or similar designation at the beginning of the article or post.

Sponsored content represents a paid commercial relationship where:
\begin{itemize}
  \item A company has paid for the creation and publication of content
  \item The content may focus on their products, services, or industry
  \item The sponsor may have input on the content's subject matter or messaging
\end{itemize}

Despite these commercial arrangements, we maintain editorial control and will only publish sponsored content that we believe provides value to our audience. Opinions expressed remain honest and authentic.

\subsection{Display Advertising}
We may display advertisements on krisyotam.com through various advertising networks or direct partnerships. These advertisements are typically identified by their placement and design as distinct from our editorial content. We do not necessarily endorse the products or services advertised on our site through these networks.

\subsection{Product Reviews and Recommendations}
We may review or recommend products and services on krisyotam.com. In some cases:
\begin{itemize}
  \item We may receive free products or services for review purposes
  \item We may earn a commission if you purchase a recommended product through our affiliate links
  \item We may have ongoing business relationships with companies whose products we review
\end{itemize}

Regardless of these relationships, we strive to provide honest, unbiased assessments. Receipt of free products or potential commissions does not guarantee positive reviews or recommendations.

\section{Identification of Commercial Content}
We are committed to transparency in our commercial relationships. To that end:
\begin{itemize}
  \item Affiliate links may be identified with a disclosure statement near the link or at the beginning or end of the content that contains such links
  \item Sponsored posts are clearly labeled as such
  \item Content that includes free products received for review will disclose this relationship
  \item Endorsements will note any material connection to the endorsed product or service
\end{itemize}

\section{No Guarantee of Results}
Products, services, or methods that we mention, review, or link to may have worked for us or others, but we cannot guarantee they will work for you. Results may vary based on individual circumstances, effort, and other factors outside our control.

\section{Editorial Independence}
Despite commercial relationships, we maintain editorial independence:
\begin{itemize}
  \item We only recommend products or services we genuinely believe in
  \item Sponsors do not dictate our opinions or content strategies
  \item We prioritize reader trust over commercial relationships
  \item We may criticize products or services even from affiliate partners or sponsors if warranted
\end{itemize}

\section{Compensation Disclosure}
The compensation received from affiliate programs, sponsored content, or advertising may influence:
\begin{itemize}
  \item The specific products or services we choose to write about
  \item The prioritization of certain content topics
  \item The timing of content publication
\end{itemize}

However, compensation does not influence our assessment of products or our commitment to providing valuable, accurate information to our readers.

\section{Non-Commercial Content}
The majority of content on krisyotam.com is non-commercial in nature and is created without direct monetary compensation from third parties. This content reflects personal interests, research, creative works, or information we believe will be valuable to our audience.

\section{Changes to Monetization Practices}
Our monetization strategies may change over time. We will update this disclosure accordingly to reflect current practices. The date at the top of this document indicates when it was last revised.

\section{Your Choices}
You are under no obligation to click on affiliate links or engage with sponsored content. If you prefer not to support krisyotam.com through these monetization methods, you can:
\begin{itemize}
  \item Navigate directly to retailer websites rather than using our affiliate links
  \item Skip content marked as sponsored
  \item Support the site through direct methods, if available (e.g., paid subscriptions, donations)
\end{itemize}

\section{FTC Compliance Statement}
This disclosure is provided in accordance with the Federal Trade Commission's 16 CFR, Part 255: "Guides Concerning the Use of Endorsements and Testimonials in Advertising" and similar regulations in other jurisdictions. We are committed to honest and transparent communication about our commercial relationships.

\section{Contact Information}
If you have questions about our advertising relationships or affiliate partnerships, please contact us at:
\begin{quote}
  Kris Yotam\\
  \href{mailto:advertising@krisyotam.com}{advertising@krisyotam.com}
\end{quote}

\end{document}
