%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%- Packages -%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%- Title formatting -%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%- Header / Footer -%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%- Document -%
\begin{document}
\onehalfspacing

%- Title block -%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Cookie \& Tracking Notice}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%- Preamble & Keywords -%
\noindent\textbf{Preamble}\\
This Cookie \& Tracking Notice explains how krisyotam.com ("we," "us," or "our") uses cookies and similar technologies to recognize you when you visit our website at krisyotam.com ("Site"). It explains what these technologies are and why we use them, as well as your rights to control our use of them.

\vspace{0.75em}
\noindent\textit{Keywords:} Cookies; Tracking Technologies; Consent; Analytics; Privacy

\vspace{1.5em}

%- Main sections -%
\section{What Are Cookies?}
Cookies are small data files that are placed on your computer or mobile device when you visit a website. Cookies are widely used by website owners to make their websites work, or to work more efficiently, as well as to provide reporting information.

Cookies set by the website owner (in this case, krisyotam.com) are called "first-party cookies." Cookies set by parties other than the website owner are called "third-party cookies." Third-party cookies enable third-party features or functionality to be provided on or through the website (such as advertising, interactive content, and analytics). The parties that set these third-party cookies can recognize your device both when it visits the website in question and also when it visits certain other websites.

\section{Why Do We Use Cookies?}
We use first-party and third-party cookies for several reasons. Some cookies are required for technical reasons in order for our Site to operate, and we refer to these as "essential" or "strictly necessary" cookies. Other cookies enable us to track and target the interests of our users to enhance the experience on our Site. We also use cookies to measure and analyze visitor behavior, improve our content and services, and remember your preferences.

\section{Types of Cookies We Use}

\subsection{Essential Cookies}
These cookies are strictly necessary to provide you with services available through our Site and to use some of its features, such as access to secure areas. Because these cookies are strictly necessary to deliver the Site, you cannot refuse them without impacting how our Site functions.

\begin{itemize}
  \item Purpose: Site functionality and security
  \item Duration: Session-based or short-term (typically 24 hours to 2 weeks)
  \item First/Third Party: First-party
\end{itemize}

\subsection{Analytics and Performance Cookies}
These cookies allow us to count visits and traffic sources so we can measure and improve the performance of our Site. They help us know which pages are the most and least popular and see how visitors move around the Site.

\begin{itemize}
  \item Purpose: Analyzing site usage to improve content and user experience
  \item Service: Seline Analytics (self-hosted analytics solution)
  \item Data Collected: Page views, time on site, navigation paths, referring sites, approximate location (country/region)
  \item Duration: Up to 12 months
  \item First/Third Party: First-party
\end{itemize}

\subsection{Functionality Cookies}
These cookies enable the Site to provide enhanced functionality and personalization. They may be set by us or by third-party providers whose services we have added to our pages.

\begin{itemize}
  \item Purpose: Remember user preferences and settings
  \item Duration: Persistent (typically 1-12 months)
  \item First/Third Party: First-party and potentially third-party for embedded content
\end{itemize}

\subsection{Third-Party Embedded Content Cookies}
Our Site occasionally includes embedded content from third-party services (like YouTube videos, academic paper PDFs, or iframe references). These third parties may place cookies on your device when you interact with their content.

\begin{itemize}
  \item Purpose: Enable functionality of embedded media or content
  \item Duration: Varies based on the third-party provider
  \item First/Third Party: Third-party
\end{itemize}

\section{How You Can Control Cookies}

\subsection{Cookie Consent}
When you first visit our Site, we may present you with a cookie consent banner (for users in jurisdictions where this is required, such as the EU and UK). This allows you to consent to or reject non-essential cookies. Essential cookies will still be placed regardless of your choice, as they are necessary for the Site to function.

\subsection{Browser Controls}
Most web browsers allow you to control cookies through their settings preferences. You can typically:

\begin{itemize}
  \item Delete cookies from your browser
  \item Block cookies by activating the setting on your browser that allows you to refuse cookies
  \item Set your browser to alert you when cookies are being sent
  \item Browse in "private" or "incognito" mode where cookies are deleted after your session
\end{itemize}

To find out more about cookies, including how to see what cookies have been set and how to manage and delete them, visit \href{http://www.allaboutcookies.org}{www.allaboutcookies.org}.

\subsection{Do Not Track}
Some browsers have a "Do Not Track" feature that signals to websites that you do not want to have your online activities tracked. Due to the lack of a common standard for interpreting these signals, our Site currently does not respond to "Do Not Track" signals. However, you can control tracking technologies through other methods described in this notice.

\section{Specific Tracking Technologies We Use}

\subsection{Local Storage}
In addition to cookies, we may use browser local storage to enhance your experience on our Site. Local storage allows websites to store larger amounts of data (such as user preferences or content states) on your device.

\begin{itemize}
  \item Purpose: Store user preferences or site state information
  \item Duration: Until cleared by the user or the website
  \item First/Third Party: First-party
\end{itemize}

\subsection{Analytics Implementation}
Our Site uses Seline Analytics, a privacy-focused analytics platform. Unlike many other analytics providers, Seline is designed to respect user privacy while still providing us with the insights we need to improve our Site. Here's how we've configured it:

\begin{itemize}
  \item IP addresses are anonymized (we only see the country/region, not the full IP address)
  \item No cross-site tracking is performed
  \item Data is stored only for the duration necessary for analysis purposes
\end{itemize}

\section{Updates to this Cookie Notice}
We may update this Cookie \& Tracking Notice from time to time in order to reflect changes to the cookies and other technologies we use or for other operational, legal, or regulatory reasons. Please re-visit this Cookie Notice regularly to stay informed about our use of cookies and related technologies.

The date at the top of this Cookie Notice indicates when it was last updated.

\section{Contact Us}
If you have any questions about our use of cookies or other tracking technologies, please contact us at:

\begin{quote}
  Kris Yotam\\
  \href{mailto:privacy@krisyotam.com}{privacy@krisyotam.com}
\end{quote}

\end{document}
