%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%- Packages -%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%- Title formatting -%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%- Header / Footer -%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%- Document -%
\begin{document}
\onehalfspacing

%- Title block -%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Copyright \& Content Ownership Statement}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%- Preamble & Keywords -%
\noindent\textbf{Preamble}\\
This Copyright \& Content Ownership Statement sets forth the rights and permissions associated with the content found on krisyotam.com ("the Site"). This statement explains who owns the intellectual property on the Site and what permissions are granted to users for different types of content.

\vspace{0.75em}
\noindent\textit{Keywords:} Copyright; Intellectual Property; Content Usage; Attribution Requirements; Creative Commons

\vspace{1.5em}

%- Main sections -%
\section{General Copyright Notice}
Unless otherwise specified, all content on this Site is © 2025 Kris Yotam. All rights reserved. This includes, but is not limited to, text, graphics, logos, images, audio clips, video clips, and data compilations.

\section{Content Categories and Usage Permissions}
The Site contains different types of content with varying usage permissions. Please reference the specific category below to understand what you may or may not do with our content.

\subsection{Original Written Works}
Original essays, blog posts, research papers, poems, and other written content created by the site owner (Kris Yotam) are protected by copyright.
\begin{itemize}
  \item \textbf{Usage Permission:} All rights reserved. You may not reproduce, distribute, modify, or otherwise use this content without express written permission, except for brief quotations with proper attribution in non-commercial contexts (such as academic papers, personal blogs, or social media with limited extracts).
  \item \textbf{Attribution:} If permitted to quote or reference: "Source: [Title of Content], Kris Yotam, krisyotam.com, [Year]"
\end{itemize}

\subsection{AI-Generated Content}
Content that is clearly identified as being generated with the assistance of AI models (including writings produced by fine-tuned models like Kelex).
\begin{itemize}
  \item \textbf{Usage Permission:} This content may be reused or adapted for any purpose, provided proper attribution is given (similar to a Creative Commons Attribution license).
  \item \textbf{Attribution:} "Source: [Title of Content], AI-generated content from krisyotam.com, [Year]"
\end{itemize}

\subsection{Images and Photographs}
Original photographs and images created by or owned by the site owner.
\begin{itemize}
  \item \textbf{Usage Permission:} May be reused with proper attribution for both commercial and non-commercial purposes, provided they are not used in a misleading or defamatory context.
  \item \textbf{Attribution:} "Photo: Kris Yotam, krisyotam.com" or "Image courtesy of krisyotam.com"
\end{itemize}

\subsection{Original Artwork and Illustrations}
Original artwork, illustrations, and graphic designs created by the site owner.
\begin{itemize}
  \item \textbf{Usage Permission:} All rights reserved. May not be reproduced, distributed, or used without explicit written permission.
  \item \textbf{To Request Permission:} Contact \href{mailto:copyright@krisyotam.com}{copyright@krisyotam.com} with details of your intended use.
\end{itemize}

\subsection{Code and Software}
Code examples, snippets, or software projects explicitly marked as open source.
\begin{itemize}
  \item \textbf{Usage Permission:} Released under the MIT License unless otherwise stated.
  \item \textbf{MIT License Terms:} Permission is granted, free of charge, to any person obtaining a copy of this software and associated documentation files, to deal in the software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the software, subject to including the copyright notice and permission notice in all copies or substantial portions of the software.
  \item \textbf{Disclaimer:} The code is provided "as is" without warranty of any kind.
\end{itemize}
Any code not explicitly marked as open source is protected under standard copyright (all rights reserved) and requires permission for use.

\section{User-Generated Content}
Comments or other content submitted by users to the Site.
\begin{itemize}
  \item \textbf{Ownership:} Users retain copyright to comments and other content they submit to the Site.
  \item \textbf{License:} By submitting content, users grant the Site owner a perpetual, non-exclusive, royalty-free license to publish, display, modify, and distribute the content in connection with the operation of the Site.
\end{itemize}

\section{Attribution Requirements}
For all content that permits reuse with attribution (such as AI-generated content, photographs, or code under the MIT License), proper attribution must be provided as specified in the relevant content category above.

When using content online, attribution should include a hyperlink to the original source when possible. If content has been modified or adapted, your attribution should indicate that changes have been made (e.g., "Based on content from krisyotam.com, with modifications").

\section{Third-Party Content}
The Site may include content owned by third parties, such as:
\begin{itemize}
  \item Embedded videos or media
  \item Academic papers or research referenced via iframe
  \item Third-party images or quotations used under fair use provisions
\end{itemize}

Such content remains the intellectual property of its respective owners. Any third-party trademarks, service marks, logos, or trade names appearing on the Site are the property of their respective owners.

\section{Fair Use Notice}
This Site contains copyrighted material the use of which has not always been specifically authorized by the copyright owner. We make such material available for criticism, comment, news reporting, teaching, scholarship, or research. We believe this constitutes a "fair use" of any such copyrighted material as provided in section 107 of the US Copyright Law.

If you are a copyright owner and wish to have your content removed from this Site, please refer to our DMCA Policy for the proper procedure to follow.

\section{Creative Commons Licensing}
While most original content on this Site is protected under standard copyright (all rights reserved), specific content may occasionally be released under Creative Commons licenses. When this is the case, the specific license will be clearly indicated alongside that content.

\section{Rights Enforcement}
We reserve the right to enforce our copyright and intellectual property rights to the fullest extent of the law. Unauthorized use of our content may result in cease-and-desist notices, DMCA takedown notices, or other legal actions.

\section{Permission Requests}
If you wish to use any content from this Site in a manner not permitted by this Copyright Statement, please contact us to request permission:

\begin{quote}
  Kris Yotam\\
  \href{mailto:copyright@krisyotam.com}{copyright@krisyotam.com}
\end{quote}

Please include:
\begin{itemize}
  \item A specific description of the content you wish to use
  \item How you intend to use it
  \item Where it will be published or displayed
  \item The duration of use
\end{itemize}

\section{Changes to This Statement}
We reserve the right to modify this Copyright \& Content Ownership Statement at any time. Any changes will be reflected on this page with an updated "Last Updated" date.

\end{document}
