%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%- Packages -%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%- Title formatting -%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%- Header / Footer -%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%- Document -%
\begin{document}
\onehalfspacing

%- Title block -%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Disclaimers}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%- Preamble & Keywords -%
\noindent\textbf{Preamble}\\
This document sets forth important disclaimers and limitations regarding the content, information, and services provided on krisyotam.com. These disclaimers are designed to clarify the nature of the content provided and to limit potential liability. By accessing and using krisyotam.com, you acknowledge and accept these disclaimers.

\vspace{0.75em}
\noindent\textit{Keywords:} Disclaimers; Not Professional Advice; Accuracy; Liability; External Links

\vspace{1.5em}

%- Main sections -%
\section{General Content Disclaimer}
The information, content, and materials available on krisyotam.com are provided "as is" and "as available" without any warranties of any kind, either express or implied. Kris Yotam does not warrant that the website or any of its contents will be uninterrupted, error-free, or free from harmful components.

To the fullest extent permitted by applicable law, Kris Yotam disclaims all warranties, express or implied, including but not limited to, implied warranties of merchantability, fitness for a particular purpose, and non-infringement.

The content on krisyotam.com is intended for general informational and entertainment purposes only. While we strive for accuracy and thoroughness, we make no representations or warranties about the completeness, reliability, suitability, or availability of the information, products, services, or related graphics contained on the website.

\section{Not Professional Advice}
\subsection{Not Legal Advice}
No content on krisyotam.com constitutes legal advice. The legal information provided is general in nature and may not apply to your specific situation. It should not be relied upon in place of consultation with qualified legal professionals. If you require legal advice, you should consult with a licensed attorney in your jurisdiction.

\subsection{Not Financial Advice}
Information related to finance, investments, cryptocurrencies, or economics on krisyotam.com does not constitute financial advice. Any financial or investment information is for informational purposes only and should not be construed as recommendations or endorsements. You should consult with qualified financial advisors before making investment decisions. Past performance is not indicative of future results, and all investments involve risk.

\subsection{Not Medical Advice}
Content on krisyotam.com related to health, wellness, or medical topics does not constitute medical advice, diagnosis, or treatment. The information provided is not intended to replace professional medical advice, diagnosis, or treatment. Always seek the advice of a physician or other qualified healthcare provider with any questions you may have regarding a medical condition or treatment.

\subsection{Not Technical/Professional Consulting}
Code examples, technical tutorials, and programming advice shared on krisyotam.com are provided for educational purposes only. We do not guarantee the security, effectiveness, or applicability of any code or technical solution in production environments. Users implement such solutions at their own risk and should conduct their own security reviews and testing. No professional consulting relationship is established by your use of these materials.

\section{Academic and Research Content Disclaimer}
Research papers, analyses, and academic content on krisyotam.com may represent ongoing work, personal interpretation, or theoretical exploration. Such content:
\begin{itemize}
  \item May not have undergone formal peer review
  \item May present preliminary findings subject to revision
  \item Should be considered as exploratory rather than definitive
  \item May represent the personal academic interests or views of the author(s)
\end{itemize}

Readers should apply appropriate skepticism and consult primary sources and peer-reviewed literature for authoritative information in academic fields.

\section{AI-Generated Content Disclaimer}
Some content on krisyotam.com may be created with the assistance of artificial intelligence. While we review and edit AI-generated content, such content:
\begin{itemize}
  \item May contain inaccuracies or errors
  \item Represents machine learning outputs rather than human expertise
  \item Should not be considered as authoritative as human-reviewed academic or professional literature
\end{itemize}

Content with substantial AI contribution is labeled as such. Please see our AI Transparency Statement for more information about our use of AI technologies.

\section{Experimental Features and Beta Content}
Features or content marked as "experimental," "beta," or "in development" are provided for testing and feedback purposes and may:
\begin{itemize}
  \item Contain bugs or errors
  \item Change significantly or be removed without notice
  \item Not work as intended in all environments or use cases
  \item Not meet the same quality standards as finalized content
\end{itemize}

Use of such features or reliance on such content is at your own risk.

\section{External Links Disclaimer}
krisyotam.com may contain links to external websites or resources that are not owned or controlled by Kris Yotam. We have no control over, and assume no responsibility for:
\begin{itemize}
  \item The content, privacy policies, or practices of any third-party websites or services
  \item The availability or security of linked sites
  \item Any damage or loss allegedly caused by or in connection with the use of any external content, goods, or services
\end{itemize}

Links are provided for convenience and information purposes only. The inclusion of any link does not imply endorsement, approval, or control by Kris Yotam of the linked site or any association with its operators.

\section{Accuracy and Currency of Information}
While we make reasonable efforts to ensure the accuracy of information on krisyotam.com, we cannot guarantee that all content is completely current or error-free. Information may become outdated over time, and technological developments, research findings, or changes in laws and regulations may supersede certain content.

Users are encouraged to verify time-sensitive information and to check the publication or update date of content.

\section{User-Generated Content Disclaimer}
Comments, forum posts, and other user-generated content on krisyotam.com are the views and opinions of their respective authors and do not necessarily reflect the official policy or position of Kris Yotam. User-generated content is not reviewed for accuracy and should not be treated as authoritative.

\section{Security Disclaimer}
While we implement reasonable security measures, we cannot guarantee that krisyotam.com is free from vulnerabilities or immune to security breaches. Users interact with our site at their own risk and should take appropriate precautions to protect their personal information and devices.

\section{Limitation of Liability}
TO THE MAXIMUM EXTENT PERMITTED BY APPLICABLE LAW, KRIS YOTAM AND/OR ITS AFFILIATES SHALL NOT BE LIABLE FOR ANY INDIRECT, INCIDENTAL, SPECIAL, CONSEQUENTIAL, OR PUNITIVE DAMAGES, INCLUDING WITHOUT LIMITATION, LOSS OF PROFITS, DATA, USE, GOODWILL, OR OTHER INTANGIBLE LOSSES, RESULTING FROM:
\begin{itemize}
  \item YOUR ACCESS TO OR USE OF OR INABILITY TO ACCESS OR USE THE SITE
  \item ANY CONDUCT OR CONTENT OF ANY THIRD PARTY ON THE SITE
  \item ANY CONTENT OBTAINED FROM THE SITE
  \item UNAUTHORIZED ACCESS, USE, OR ALTERATION OF YOUR TRANSMISSIONS OR CONTENT
\end{itemize}

REGARDLESS OF THE THEORY OF LIABILITY, WHETHER BASED IN CONTRACT, TORT, NEGLIGENCE, STRICT LIABILITY, OR OTHERWISE, AND EVEN IF KRIS YOTAM HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.

\section{Indemnification}
You agree to defend, indemnify, and hold harmless Kris Yotam from and against any claims, liabilities, damages, losses, and expenses, arising out of or in any way connected with your access to or use of krisyotam.com or your violation of these Disclaimers.

\section{Modifications to Disclaimers}
Kris Yotam reserves the right to modify these disclaimers at any time, effective upon posting the updated version on krisyotam.com. Please check this page periodically for changes.

\section{Contact Information}
If you have any questions about these disclaimers, please contact:
\begin{quote}
  Kris Yotam\\
  \href{mailto:legal@krisyotam.com}{legal@krisyotam.com}
\end{quote}

\end{document}
