%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%- Packages -%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%- Title formatting -%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%- Header / Footer -%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%- Document -%
\begin{document}
\onehalfspacing

%- Title block -%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries DMCA Policy}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%- Preamble & Keywords -%
\noindent\textbf{Preamble}\\
This Digital Millennium Copyright Act (DMCA) Policy outlines the procedures for submitting and responding to claims of copyright infringement on krisyotam.com. We respect the intellectual property rights of others and expect our users to do the same. This policy explains how copyright owners can report potentially infringing content and how we will process such reports.

\vspace{0.75em}
\noindent\textit{Keywords:} Copyright Infringement; Takedown Notice; Counter-Notice; Safe Harbor; Intellectual Property

\vspace{1.5em}

%- Main sections -%
\section{Designated Agent Information}
In accordance with the Digital Millennium Copyright Act (17 U.S.C. § 512), the following person has been designated to receive notifications of claimed copyright infringement on behalf of krisyotam.com:

\begin{quote}
  DMCA Agent: Kris Yotam\\
  Email: \href{mailto:dmca@krisyotam.com}{dmca@krisyotam.com}\\
  Address: [Physical mailing address available upon legitimate request]
\end{quote}

\section{How to File a DMCA Takedown Notice}
If you believe that content on krisyotam.com infringes your copyright, you may submit a notification pursuant to the DMCA. To be effective, your notification must include the following information:

\begin{enumerate}
  \item A physical or electronic signature of a person authorized to act on behalf of the owner of an exclusive right that is allegedly infringed.
  
  \item Identification of the copyrighted work claimed to have been infringed, or, if multiple copyrighted works on our site are covered by a single notification, a representative list of such works.
  
  \item Identification of the material that is claimed to be infringing or to be the subject of infringing activity and that is to be removed or access to which is to be disabled, and information reasonably sufficient to permit us to locate the material. Providing URLs in the body of an email is the best way to help us locate content quickly.
  
  \item Information reasonably sufficient to permit us to contact you, such as an address, telephone number, and, if available, an email address.
  
  \item A statement that you have a good faith belief that use of the material in the manner complained of is not authorized by the copyright owner, its agent, or the law.
  
  \item A statement that the information in the notification is accurate, and under penalty of perjury, that you are authorized to act on behalf of the owner of an exclusive right that is allegedly infringed.
\end{enumerate}

You may send your DMCA notification to our Designated Agent via email or mail using the contact information provided above.

\section{Upon Receipt of a Valid DMCA Notice}
Upon receiving a valid DMCA takedown notice, we will:

\begin{enumerate}
  \item Promptly remove or disable access to the allegedly infringing material.
  
  \item Make a good-faith effort to notify the user who posted the content that it has been removed or disabled.
  
  \item Provide the user with a copy of the takedown notice and inform them that they may submit a counter-notice if they believe the content was removed in error.
  
  \item Take reasonable steps to promptly notify the complaining party that we have removed or disabled access to the material.
\end{enumerate}

We aim to process valid DMCA notices within 5-10 business days of receipt.

\section{Counter-Notification Process}
If you believe that your content was removed due to a mistake or misidentification, you may submit a counter-notice to our Designated Agent. To be effective, a counter-notice must include the following information:

\begin{enumerate}
  \item Your physical or electronic signature.
  
  \item Identification of the material that has been removed or to which access has been disabled and the location at which the material appeared before it was removed or access to it was disabled.
  
  \item A statement under penalty of perjury that you have a good faith belief that the material was removed or disabled as a result of mistake or misidentification of the material to be removed or disabled.
  
  \item Your name, address, and telephone number, and a statement that you consent to the jurisdiction of Federal District Court for the judicial district in which your address is located, or if your address is outside of the United States, for any judicial district in which krisyotam.com may be found, and that you will accept service of process from the person who provided the original notification or an agent of such person.
\end{enumerate}

\section{Upon Receipt of a Valid Counter-Notice}
Upon receiving a valid counter-notice, we will:

\begin{enumerate}
  \item Promptly provide the complaining party with a copy of the counter-notice.
  
  \item Inform the complaining party that we will restore the removed material in 10-14 business days unless we receive notice that the complaining party has filed a court action seeking to restrain the user from engaging in infringing activity related to the removed material.
  
  \item Restore the removed material between 10 and 14 business days after receiving the counter-notice, unless we receive notice of legal action from the complaining party.
\end{enumerate}

\section{Repeat Infringer Policy}
In accordance with the DMCA, we have adopted a policy to terminate, in appropriate circumstances, users who are deemed to be repeat infringers. We may also, at our sole discretion, limit access to krisyotam.com and/or terminate the accounts of any users who infringe any intellectual property rights of others, whether or not there is any repeat infringement.

\section{False Claims and Misrepresentations}
Filing a false DMCA notice or counter-notice may have serious legal consequences. Under Section 512(f) of the DMCA, any person who knowingly materially misrepresents that material is infringing, or that it was removed or disabled by mistake or misidentification, shall be liable for any damages, including costs and attorneys' fees, incurred by the alleged infringer or the copyright owner as a result of such misrepresentation.

\section{Good Faith Belief}
Before submitting a DMCA notice, consider whether the use of your copyrighted material might be protected by the "fair use" doctrine. Fair use permits limited use of copyrighted material without authorization for purposes such as criticism, comment, news reporting, teaching, scholarship, or research.

\section{Standard Technical Measures}
krisyotam.com accommodates and does not interfere with standard technical measures used by copyright owners to identify or protect copyrighted works.

\section{International Considerations}
Although the DMCA is a United States law, we respect the intellectual property rights of creators worldwide. If you are outside of the United States and believe your copyright is being infringed on our site, you may submit a notice following the procedures outlined above. We will respond to all valid notices, regardless of geographic origin.

\section{Modifications to this Policy}
We reserve the right to modify this DMCA Policy at any time. Any changes will be reflected on this page with a new "Last Updated" date.

\section{Contact Information}
If you have any questions about this DMCA Policy, please contact us at:
\begin{quote}
  Kris Yotam\\
  \href{mailto:dmca@krisyotam.com}{dmca@krisyotam.com}
\end{quote}

\end{document}
