%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%-- Packages --%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%-- Title formatting --%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%-- Header / Footer --%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%-- Document --%
\begin{document}
\onehalfspacing

%-- Title block --%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Privacy Policy}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%-- Preamble & Keywords --%
\noindent\textbf{Preamble}\\
This Privacy Policy describes how your personal information is collected, used, and shared when you visit krisyotam.com (the "Site"). We respect your privacy and are committed to protecting your personal data in accordance with applicable privacy laws, including the EU General Data Protection Regulation (GDPR), UK GDPR, the California Consumer Privacy Act (CCPA), and other applicable regulations.

\vspace{0.75em}
\noindent\textit{Keywords:} Privacy Policy; Data Collection; User Rights; GDPR; CCPA

\vspace{1.5em}

%-- Main sections --%
\section{Data Controller}
Kris Yotam is the data controller responsible for your personal data collected through this Site. For all privacy-related inquiries, please contact:

\begin{quote}
  Kris Yotam\\
  \href{mailto:privacy@krisyotam.com}{privacy@krisyotam.com}
\end{quote}

\section{Information We Collect}

\subsection{Personal Information You Provide}
We may collect the following types of personal information that you voluntarily provide to us:
\begin{itemize}
  \item Email address (when subscribing to newsletters or submitting contact forms)
  \item Name (when provided in comments or contact forms)
  \item Comments or message content you choose to submit
  \item Information you provide when participating in surveys or feedback requests
\end{itemize}

\subsection{Information Automatically Collected}
When you visit the Site, we automatically collect certain information about your device, including:
\begin{itemize}
  \item IP address
  \item Browser type and version
  \item Operating system
  \item Time and date of your visit
  \item Pages viewed and time spent on pages
  \item Referring website or source
  \item Technical information about your interaction with our Site
\end{itemize}

We collect this information using cookies and similar technologies. For more information about our use of cookies, please see our Cookie \& Tracking Notice.

\section{How We Use Your Information}

We use the information we collect for the following purposes:

\subsection{Personal Information You Provide}
\begin{itemize}
  \item To provide and maintain the Service
  \item To send newsletters and updates to subscribers
  \item To respond to inquiries and provide support
  \item To process and fulfill any transactions or services requested
  \item To improve our content and services based on your feedback
  \item To send administrative information, such as updates to our terms or privacy policy
\end{itemize}

\subsection{Information Automatically Collected}
\begin{itemize}
  \item To analyze usage patterns and improve the Site
  \item To prevent fraud, protect the security of our Site, and address technical issues
  \item To fulfill our legitimate interests in understanding how users interact with our Site
  \item To maintain and improve the functionality and performance of the Site
\end{itemize}

\section{Legal Basis for Processing (EU/UK Users)}

For users from the European Economic Area (EEA) and UK, we process your personal data on the following legal grounds:
\begin{itemize}
  \item Consent: When you explicitly consent to the processing (e.g., by subscribing to a newsletter)
  \item Legitimate Interest: When necessary for our legitimate interests (such as analyzing Site usage to improve our content), provided these interests are not overridden by your data protection rights
  \item Contractual Necessity: When necessary to fulfill a contract with you (e.g., when you purchase digital products)
  \item Legal Obligation: When necessary to comply with a legal obligation
\end{itemize}

\section{Sharing Your Information}

We do not sell your personal information to advertisers or other third parties. However, we may share your information with:

\subsection{Service Providers}
We use third-party service providers to help us operate our Site, including:
\begin{itemize}
  \item Seline Analytics (for site analytics)
  \item Substack (for newsletter management)
  \item Payment processors for handling transactions (if applicable)
\end{itemize}

These service providers have access to your personal information only to perform specific tasks on our behalf and are obligated not to disclose or use it for any other purpose.

\subsection{Legal Requirements}
We may disclose your information if required to do so by law or in response to valid requests by public authorities (e.g., a court or government agency).

\section{Data Retention}

We will retain your information only for as long as necessary to fulfill the purposes outlined in this Privacy Policy, unless a longer retention period is required or permitted by law. Specifically:
\begin{itemize}
  \item Newsletter subscription data: Until you unsubscribe
  \item Comments: Indefinitely unless deletion is requested
  \item Contact form submissions: Up to 1 year after resolution of your inquiry
  \item Analytics data: In identifiable form for up to 12 months, after which it may be aggregated or anonymized
\end{itemize}

\section{International Data Transfers}

The Site is operated in the United States. If you are located in the European Economic Area (EEA), UK, or other regions with data protection laws that may differ from those in the United States, please be aware that information we collect may be transferred to, stored, and processed in the United States.

By using our Site or providing us with any information, you consent to this transfer, storage, and processing. We will take all steps reasonably necessary to ensure that your data is treated securely and in accordance with this Privacy Policy and applicable data protection laws. Where necessary, we rely on Standard Contractual Clauses or other valid transfer mechanisms to transfer data internationally.

\section{Your Rights}

Depending on your location, you may have certain rights regarding your personal information:

\subsection{For All Users}
\begin{itemize}
  \item Right to access and receive information about the personal information we collect about you
  \item Right to correct inaccurate information
  \item Right to unsubscribe from marketing communications
\end{itemize}

\subsection{For EU/UK Users (GDPR)}
\begin{itemize}
  \item Right to access your personal data
  \item Right to rectification of inaccurate data
  \item Right to erasure ("right to be forgotten")
  \item Right to restriction of processing
  \item Right to data portability
  \item Right to object to processing based on legitimate interests
  \item Right to withdraw consent at any time
  \item Right to lodge a complaint with a supervisory authority
\end{itemize}

\subsection{For California Residents (CCPA/CPRA)}
\begin{itemize}
  \item Right to know what personal information is collected, used, shared, or sold
  \item Right to delete personal information held by businesses
  \item Right to opt-out of the sale of personal information
  \item Right to non-discrimination for exercising your CCPA rights
\end{itemize}

To exercise any of these rights, please contact us at \href{mailto:privacy@krisyotam.com}{privacy@krisyotam.com}. We will respond to your request within a reasonable timeframe (within 30 days for most requests).

\section{Children's Privacy}

Our Site is not intended for children under 13 years of age, and we do not knowingly collect personal information from children under 13. If you are a parent or guardian and believe that your child has provided us with personal information, please contact us immediately. If we become aware that we have collected personal information from children without verification of parental consent, we will take steps to remove that information from our servers.

\section{Do Not Track Signals}

Some browsers have a "Do Not Track" feature that signals to websites that you do not want to have your online activities tracked. Due to the lack of a common standard for interpreting these signals, our Site currently does not respond to "Do Not Track" signals.

\section{Third-Party Links}

Our Site may contain links to other websites that are not operated by us. If you click on a third-party link, you will be directed to that third party's site. We strongly advise you to review the Privacy Policy of every site you visit. We have no control over and assume no responsibility for the content, privacy policies, or practices of any third-party sites or services.

\section{Changes to This Privacy Policy}

We may update this Privacy Policy from time to time. We will notify you of any changes by posting the new Privacy Policy on this page and updating the "Last Updated" date. You are advised to review this Privacy Policy periodically for any changes. Changes to this Privacy Policy are effective when they are posted on this page.

\section{Contact Us}

If you have any questions about this Privacy Policy or our privacy practices, please contact us at:
\begin{quote}
  Kris Yotam\\
  \href{mailto:privacy@krisyotam.com}{privacy@krisyotam.com}
\end{quote}

\end{document}
