%-----------------------------%
% Template 4c: Legal Document Template
%-----------------------------%
\documentclass[11pt]{article}

%-- Packages --%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

%-- Title formatting --%
\newcommand{\TitleLine}{\noindent\rule{\textwidth}{0.4pt}}
\titleformat*{\section}{\bfseries\normalsize}
\titleformat*{\subsection}{\bfseries\normalsize}

%-- Header / Footer --%
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\itshape © 2025 Kris Yotam}
\fancyfoot[R]{\itshape Last Updated: May 23, 2025}
\fancyfoot[C]{\thepage}

%-- Document --%
\begin{document}
\onehalfspacing

%-- Title block --%
\vspace*{-1em}
\TitleLine
\vspace{0.5em}
\begin{center}
  {\Large\bfseries Terms of Service}\\[0.75em]
  {\normalsize Kris Yotam}\\
  {\itshape Illinois, United States}
\end{center}
\vspace{0.5em}
\TitleLine

\vspace{1.5em}

%-- Preamble & Keywords --%
\noindent\textbf{Preamble}\\
These Terms of Service ("Terms") govern your access to and use of the website and related services operated by Kris Yotam ("we", "us", "our") at krisyotam.com and all associated subdomains (collectively, the "Service"). By accessing or using the Service, you agree to be bound by these Terms. If you do not agree to all of these Terms, you may not access or use the Service.

\vspace{0.75em}
\noindent\textit{Keywords:} Terms of Service; User Obligations; Content Usage; Liability Limitations

\vspace{1.5em}

%-- Main sections --%
\section{Definitions}
\begin{itemize}
  \item \textbf{"Service"} means the krisyotam.com website, its content, features, and all related functionalities.
  \item \textbf{"User"} means any person accessing or using the Service.
  \item \textbf{"Content"} means text, images, videos, code, or any other materials provided through the Service.
  \item \textbf{"User Content"} means any content, including comments, feedback, or other materials, submitted or posted by Users.
\end{itemize}

\section{Acceptance of Terms}
By using the Service, you acknowledge that you have read, understood, and agree to these Terms in full. You also agree to our Privacy Policy, Cookie \& Tracking Notice, and other policies referenced herein. We reserve the right to modify these Terms at any time, with changes effective upon posting. Your continued use of the Service after changes constitutes acceptance of the updated Terms.

\section{User Obligations}
You agree not to:
\begin{itemize}
  \item Violate any applicable laws or regulations.
  \item Attempt to gain unauthorized access to any portion of the Service.
  \item Upload content that infringes upon third-party rights.
  \item Post spam, malicious content, or engage in disruptive behavior.
  \item Use the Service to transmit viruses, malware, or other harmful code.
  \item Harass, threaten, or cause distress or discomfort to other users.
  \item Impersonate others or misrepresent your affiliation with any person or entity.
  \item Collect or harvest personal information of other users.
\end{itemize}

\section{Age Restriction}
You must be at least 13 years of age to use this Service. If you are under 18, you represent that you have parental consent to access and use the Service and that your parent or guardian has reviewed and agreed to these Terms.

\section{Account Management}
If the Service allows you to create an account, you are responsible for maintaining the confidentiality of your account credentials and for all activities under your account. You agree to notify us immediately of any unauthorized use of your account. We reserve the right to terminate or suspend accounts at our discretion.

\section{Intellectual Property}
All content and materials on the Service, unless otherwise specified, are © 2025 Kris Yotam. No portion may be reproduced, distributed, modified, or otherwise used without express written permission. For permitted uses of specific content types, please refer to our Copyright \& Content Ownership Statement.

\section{User-Generated Content}
By submitting User Content to the Service (such as comments):
\begin{itemize}
  \item You retain ownership of your User Content.
  \item You grant us a worldwide, non-exclusive, royalty-free license to use, store, display, reproduce, modify, and distribute your User Content in connection with the operation of the Service.
  \item You represent that you have all rights necessary to submit such User Content and that it does not violate these Terms.
  \item You are solely responsible for your User Content and any claims arising from it.
\end{itemize}

We reserve the right to remove any User Content at our sole discretion, including content that we believe violates these Terms or is otherwise objectionable.

\section{Content Moderation}
We reserve the right to monitor, edit, or remove any content that violates these Terms or that we find objectionable for any reason, without notice. We do not guarantee that we will review all content, and our failure to remove particular content does not constitute approval or endorsement of such content.

\section{Third-Party Links and Services}
The Service may contain links to third-party websites or services that are not owned or controlled by us. We have no control over, and assume no responsibility for, the content, privacy policies, or practices of any third-party websites or services. You further acknowledge and agree that we shall not be responsible or liable, directly or indirectly, for any damage or loss caused or alleged to be caused by or in connection with the use of or reliance on any such content, goods, or services available on or through any such websites or services.

\section{Paid Services and Digital Products}
For any paid newsletters, digital products, or services offered through the Service:
\begin{itemize}
  \item All prices are as stated on the Service and may be subject to change.
  \item Payment terms, including billing cycles, will be clearly indicated before purchase.
  \item You may cancel recurring subscriptions according to the cancellation procedures provided.
  \item Unless otherwise stated, digital product sales are final and non-refundable once access has been granted.
  \item Third-party payment processors (e.g., Substack, Stripe, PayPal) may have additional terms governing payment transactions.
\end{itemize}

\section{Disclaimers and Warranties}
THE SERVICE AND ALL CONTENT ARE PROVIDED "AS IS" WITHOUT WARRANTY OF ANY KIND, EITHER EXPRESS OR IMPLIED, INCLUDING, BUT NOT LIMITED TO, IMPLIED WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE, OR NON-INFRINGEMENT. WE DO NOT GUARANTEE THAT:
\begin{itemize}
  \item THE SERVICE WILL MEET YOUR REQUIREMENTS.
  \item THE SERVICE WILL BE UNINTERRUPTED, TIMELY, SECURE, OR ERROR-FREE.
  \item THE RESULTS THAT MAY BE OBTAINED FROM THE USE OF THE SERVICE WILL BE ACCURATE OR RELIABLE.
  \item THE QUALITY OF ANY PRODUCTS, SERVICES, INFORMATION, OR OTHER MATERIAL PURCHASED OR OBTAINED THROUGH THE SERVICE WILL MEET YOUR EXPECTATIONS.
\end{itemize}

\section{Code and Technical Content Disclaimer}
Any code, technical advice, or programming examples provided on the Service are offered for educational purposes only. While we strive for accuracy, we make no guarantees regarding the suitability, security, or correctness of this content for any specific purpose. Users implement such code or advice at their own risk.

\section{Limitation of Liability}
TO THE FULLEST EXTENT PERMITTED BY LAW, WE SHALL NOT BE LIABLE FOR ANY INDIRECT, INCIDENTAL, SPECIAL, CONSEQUENTIAL, OR PUNITIVE DAMAGES, INCLUDING WITHOUT LIMITATION, LOSS OF PROFITS, DATA, USE, GOODWILL, OR OTHER INTANGIBLE LOSSES, RESULTING FROM:
\begin{itemize}
  \item YOUR ACCESS TO OR USE OF OR INABILITY TO ACCESS OR USE THE SERVICE.
  \item ANY CONDUCT OR CONTENT OF ANY THIRD PARTY ON THE SERVICE.
  \item ANY CONTENT OBTAINED FROM THE SERVICE.
  \item UNAUTHORIZED ACCESS, USE, OR ALTERATION OF YOUR TRANSMISSIONS OR CONTENT.
\end{itemize}

OUR TOTAL LIABILITY FOR ANY CLAIM ARISING FROM OR RELATING TO THESE TERMS OR OUR SERVICE IS LIMITED TO THE GREATER OF \$50 USD OR THE AMOUNT YOU PAID US IN THE PAST 12 MONTHS.

\section{Indemnification}
You agree to defend, indemnify, and hold harmless Kris Yotam and all affiliates from and against any claims, liabilities, damages, losses, and expenses, including without limitation reasonable attorney's fees and costs, arising out of or in any way connected with your access to or use of the Service or your violation of these Terms.

\section{Copyright Infringement}
We respect the intellectual property rights of others and expect users to do the same. If you believe that material on our Service infringes upon your copyright, please see our DMCA Policy for instructions on submitting a notice. We will terminate, in appropriate circumstances, users who are deemed to be repeat infringers.

\section{Governing Law}
These Terms shall be governed by and construed in accordance with the laws of the State of Illinois, without regard to its conflict of law principles. Any legal action or proceeding arising out of these Terms or your use of the Service shall be brought exclusively in the federal or state courts located in Illinois, and you consent to the personal jurisdiction of such courts.

\section{Severability}
If any provision of these Terms is found to be unenforceable or invalid, that provision will be limited or eliminated to the minimum extent necessary so that the Terms will otherwise remain in full force and effect and enforceable.

\section{Entire Agreement and Waiver}
These Terms, together with the Privacy Policy and any other legal notices published by us on the Service, shall constitute the entire agreement between you and us concerning the Service. Our failure to exercise or enforce any right or provision of these Terms shall not constitute a waiver of such right or provision.

\section{Changes to Terms}
We reserve the right to modify these Terms at any time at our sole discretion. We will provide notice of significant changes by posting the updated Terms on the Service with a new "Last Updated" date. Your continued use of the Service after such modifications constitutes your acceptance of the revised Terms.

\section{Termination}
We may terminate or suspend your access to the Service immediately, without prior notice or liability, for any reason whatsoever, including without limitation if you breach the Terms. All provisions of the Terms which by their nature should survive termination shall survive termination, including, without limitation, ownership provisions, warranty disclaimers, indemnity, and limitations of liability.

\section{Contact Information}
For questions or notices under these Terms, please contact:
\begin{quote}
  Kris Yotam\\
  \href{mailto:legal@krisyotam.com}{legal@krisyotam.com}
\end{quote}

\end{document}
